### 2017-11-17 Risk analysis/Text/Layout/Layout/chapter3_results.tex
Figures in Appendix. Next: Discussion!

		\subsection{Posterior model V: Controversial information about the Shale Smear Factor}%ML5
		In this last model simulation, no thickness likelihoods, only a $SSF$-related likelihood was used. In contrast to model IV, this was chosen to narrow the probability of the $SSF$ to be around the threshold of its critical value, by basing it on a normal distribution with a mean of 3 and a standard deviation of 0.3.\\
		Results are relatively similar to those of the prior model. It is notable that the information entropy regarding the position of layer boundaries in the footwall was decreased, while the entropy seems to have been raised significantly in the hanging wall (Figure \ref{ML5} (b)). Furthermore, an increase in the relevance of cross-fault leakage to overlying formations ("LEAK OVER") as a trap volume mechanism (increase from $\sim13\5$ to $\sim18\%$) was observed (Figure \ref{ML5} (c)). Consequently, the bimodality between the bulk of positive values and the probability of complete failure in the $ROV$ distribution was apparently reinforced. This is also indicated by a shift of mean and median to lower volumes (Figure \ref{ML5} (d)). Accordingly, a higher degree of decision divergence, i.e. a greater separation of different Bayes actions, was induced (Figure \ref{ML5} (e)). Expected losses of the minima were raised as well.\\
		It is notable that the implementation of a likelihood which can be expected to significantly decrease the $SSF$ related uncertainty, overall leads to an amplification of the duality in the $ROV$ probability distribution and to dispersion of different risk-affine decisions. This effect is presumably caused by conservation of decisive uncertainty between "success" and complete failure of the trap, by narrowing the probability of the $SSF$ to be around its critical value.

>>>>

		\subsection{Posterior model V: Controversial information about the Shale Smear Factor}%ML5
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML5}
			\caption{....}\label{fig:ML5}
		\end{figure}
		In this last case example, no thickness likelihoods, only a $SSF$-related likelihood was used. In contrast to model IV, this was chosen to narrow the probability of the $SSF$ to be around the threshold of its critical value, by basing it on a normal distribution with a mean of 3 and a standard deviation of 0.3.\\
		Results are relatively similar to those of the prior model. It is notable that the information entropy regarding the position of layer boundaries in the footwall was decreased, while the entropy seems to have been raised significantly in the hanging wall (Figure \ref{fig:ML5} (b)). Furthermore, an increase in the relevance of cross-fault leakage to overlying formations ("LEAK OVER") as a trap volume mechanism (increase from $\sim13\%$ to $\sim18\%$) was observed (Figure \ref{fig:ML5} (c)). Consequently, the bimodality between the bulk of positive values and the probability of complete failure in the $ROV$ distribution was apparently reinforced. This is also indicated by a shift of mean and median to lower volumes (Figure \ref{fig:ML5} (d)). Accordingly, a higher degree of decision divergence, i.e. a greater separation of different Bayes actions, was induced (Figure \ref{fig:ML5} (e)). Expected losses of the minima were raised as well.\\
		It is notable that the implementation of a likelihood which can be expected to significantly decrease the $SSF$ related uncertainty, overall leads to an amplification of the duality in the $ROV$ probability distribution and to dispersion of different risk-affine decisions. This effect is presumably caused by conservation of decisive uncertainty between "success" and complete failure of the trap, by narrowing the probability of the $SSF$ to be around its critical value.
